Observing Economic Growth in Unrecognized States with Nighttime Light \thanks{I thank Elizaveta Kugaevskaia for her superb research assistance on this project. Financial support from Japan Society for the Promotion of Science (JSPS Kakenhi Grant Number 17K13730) is gratefully acknowledged.}

### 2019-03-19 paper/paper.tex
Add the link to GitHub repository for replication #56
We use the cprotect package so that the verbatim can be used in the title footnote.

\usepackage{bigfoot} % Allow \verb in a footnote

% Make figure captions left-aligned: see https://tex.stackexchange.com/questions/275131/align-caption-to-the-left
\usepackage{caption} 
\captionsetup{justification=raggedright,singlelinecheck=false}

@@

\title{Observing Economic Growth in Unrecognized States with Nighttime Light \thanks{I thank Elizaveta Kugaevskaia for her superb research assistance on this project. Financial support from Japan Society for the Promotion of Science (JSPS Kakenhi Grant Number 17K13730) is gratefully acknowledged.} }
\author{Masayuki Kudamatsu \thanks{Osaka School of International Public Policy, Osaka University. Email: m.kudamatsu@gmail.com}}
\date{\today}
\maketitle

>>>>

\usepackage{bigfoot} % Allow \verb in a footnote
\usepackage{cprotect} % Allow \verb in title
% Make figure captions left-aligned: see https://tex.stackexchange.com/questions/275131/align-caption-to-the-left
\usepackage{caption} 
\captionsetup{justification=raggedright,singlelinecheck=false}

@@

\cprotect\title{
	Observing Economic Growth \\in Unrecognized States \\with Nighttime Light 
	\cprotect\thanks{%
		I thank Elizaveta Kugaevskaia for her superb research assistance on this project. 
		Financial support from Japan Society for the Promotion of Science (JSPS Kakenhi Grant Number 17K13730) is gratefully acknowledged. 
		The replication files are available at the GitHub repository for this paper: \verb!github.com/mkudamatsu/unrecognized_states!
		} 
	}
\author{Masayuki Kudamatsu \thanks{Osaka School of International Public Policy, Osaka University. Email: m.kudamatsu@gmail.com}}
\date{\today}
\maketitle
